### 2015-10-23 docs/plan.tex
Issue 1405: added new docs directory with content
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@2764 40876441-3496-0410-a613-a2fca35b2ae2

\documentclass[11pt,twoside]{article}

\setlength{\hoffset}{-1in}
\setlength{\voffset}{-1in}

\setlength{\topmargin}{2cm}
\setlength{\evensidemargin}{3.1cm}
\setlength{\oddsidemargin}{3.1cm}

\setlength{\textwidth}{14.8cm}
\setlength{\textheight}{23cm}

\setlength{\parindent}{0pt}
\setlength{\parskip}{\smallskipamount}

\newcommand{\inputkey}[1]{\framebox{\textbf{\texttt{#1}}}}
\newcommand{\e}[1]{\cdot10^{#1}}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\beqa}{\begin{eqnarray}}
\newcommand{\eeqa}{\end{eqnarray}}
\newcommand{\com}[1]{\textcolor{red}{#1}}
\newcommand{\cur}[1]{{\textit{#1}}}

\begin{document}

\setcounter{page}{1}

\tableofcontents

\newpage

\setcounter{page}{1}

@@

%\newpage
%\section{Coordination Meetings}

\begin{thebibliography}{99}
\bibitem{ieee-828-2012} IEEE Standard 828-2011 ``IEEE Standard for
Software Configuration Management Plans''
\bibitem{mpi-standard} Message Passing Interface Forum. MPI: A Message
Passing Interface Standard Version 1.3 (1998).
%\bibitem{paraview} Paraview is a standard visualisation package. 
\bibitem{apacheAPR} See, e.g., the Apache Portable Runtime Project ``APR's Version Numbering''  https://apr.apache.org/versioning.html (Accessed 2015).
\end{thebibliography}

\vfill\eject

\end{document}

>>>>

@@

%\begin{thebibliography}{99}
%\bibitem{ieee-828-2012} IEEE Standard 828-2011 ``IEEE Standard for
%Software Configuration Management Plans''
%\bibitem{mpi-standard} Message Passing Interface Forum. MPI: A Message
%Passing Interface Standard Version 1.3 (1998).
%\bibitem{paraview} Paraview is a standard visualisation package. 
%\bibitem{apacheAPR} See, e.g., the Apache Portable Runtime Project ``APR's Version Numbering''  https://apr.apache.org/versioning.html (Accessed 2015).
%\end{thebibliography}
